Capstone Movielens Report

### 2025-09-21 reports/capstone-movielens.site/01.intro.Rmd
Fix for 1.1 Datasets Overview section.

For this purpose, a dedicated package, [edx.capstone.movielens.data](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data), has been developed by the author of this report. The source code of the package is available on [GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].

Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
```{r}
if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

>>>>

For this purpose, a dedicated package, [edx.capstone.movielens.data](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data/blob/main/README.md), has been developed by the author of this report. The source code of the package is available on [GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data) (the main `R` script that prepares the necessary datasets is located in the file [init-movielens-data.R](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data/blob/main/data-raw/init-movielens-data.R))[@edx_capstone_movielens_data].

Let's install the development version of this package from the _GitHub repository_ and attach the correspondent library to the global environment:
```{r}
if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
